Binning Strategies and Related Loss for Large Data

### 2015-12-18 versionForJCGS/PaperJCGS.Rnw
little edit to wording

We now revisit the baseball data used earlier and construct binned scatterplots using specification principles developed based on loss properties from the previous sections. We begin by specifying the bin dimensions and origin for standard rectangular binning. We use integer bin widths in each dimension of spatial bins to avoid artificial density stripes because each variable is recorded as an integer, corresponding to a one game by one strike-out data resolution. We desire relatively fine binning of approximately 50 bins in each dimension; the data range from 1 to 106 games and from 0 to 513 strike-outs, thus we set bin dimensions to two games by ten strikeouts. The origin offset of $(0.5,-0.5)$ is used to shift the binning back by a half game and down by one half strikeout to adjust for the data resolution. %The data has only 42,583 observations, so we can bin on a fine grid without taking an inordinate amount of computation time. 
We find that we have approximately 3\% lower net spatial loss, after standardizing measurement units, for our binning specification using the recommended origin offset than if we were to naively set the binning origin at the minimum data values of one game and zero strikeouts.

>>>>

We now revisit the baseball data used earlier and construct binned scatterplots using the loss-based specification principles developed in the previous sections. We begin by specifying the bin dimensions and origin for standard rectangular binning. We use integer bin widths in each dimension of spatial bins to avoid artificial density stripes because each variable is recorded as an integer, corresponding to a one game by one strike-out data resolution. We desire relatively fine binning of approximately 50 bins in each dimension; the data range from 1 to 106 games and from 0 to 513 strike-outs, thus we set bin dimensions to two games by ten strikeouts. The origin offset of $(0.5,-0.5)$ is used to shift the binning back by a half game and down by one half strikeout to adjust for the data resolution. %The data has only 42,583 observations, so we can bin on a fine grid without taking an inordinate amount of computation time. 
We find that we have approximately 3\% lower net spatial loss, after standardizing measurement units, for our binning specification using the recommended origin offset than if we were to naively set the binning origin at the minimum data values of one game and zero strikeouts.
